Financialisation of Commodity Markets

### 2025-08-25 docs/paper.qmd
Made captions for bar charts

```{r}
#| label: fetch
#| include: false
#| cache: true

@@

tables_directory_path <- here::here("explore", "tables", "revision-jfm")

@@

>>>>

```{r}
#| label: fetch
#| include: false
#| cache: true
library(dplyr)
library(ggplot2)
library(here)
library(MetBrewer)
library(readr)
library(slituR)
library(tidyr)

@@

figures_directory_path <- here::here("explore", "results", "figures")
tables_directory_path <- here::here("explore", "tables", "revision-jfm")

@@

# Figures {.unnumbered}

```{r}
#| label: fig-estimates
#| fig-cap: "This figure compares the evolution of estimates for mean (top panel) and volatility (bottom panel) for individual commodity returns across three period transitions: past → financialisation, financialisation → crisis and crisis → post-crisis. Each stacked bar shows how many cases fall into two categories: yellow (the estimate in the previous period is smaller than in the next period) and blue (the estimate in the previous period is larger than in the next period); numbers inside the bars indicate the count of observations in each category. Detailed results are available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/). Period definitions are discussed in @sec-methods while the results are discussed in @sec-results."
#| fig-height: 6
#| fig-width: 5

estimates <- readr::read_rds(here::here(figures_directory_path, "estimates.rds"))
estimates
```

```{r}
#| label: fig-regimes
#| fig-cap: "This figure compares estimates for mean (top panel) and volatility (bottom panel) for individual commodity returns between **CHP** regime phases (**backwardation** vs. **contango**) for the four periods. Each stacked bar shows how many cases fall into two categories: yellow (the estimate for the **backwardation phase** is smaller than for the **contango** phase) and blue (the estimate for the **backwardation phase** is greater than for the **contango** phase); numbers inside the bars indicate the count of observations in each category. **Backwardation** and **contango** regimes as well as period definitions are discussed in @sec-methods while the results are discussed in @sec-results."
#| fig-height: 6
#| fig-width: 5

regimes <- readr::read_rds(here::here(figures_directory_path, "regimes.rds"))
regimes
```
